Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-04-04 ApJ_submit_v2/response.txt

1       x
2       x
3       x
4       x
5	x
6       x
7       x
8
9       x
10	x
11      x
12
13
14      x-abstract
15
16      x
17      x
18
19	x
20      x
21      x
22      x
23

@@

17. The discussion of the magnetic field strength needed to produce a drag that sort of makes the GCM model work the best is very wishy washy. I understand that the authors are using order-of-magnitude expressions (as they state) but I think the magnetic field discussion is oversimplified and the conclusions are overstated. It also neglects to mention previous work attempting to directly measure/detect the effects of magnetic fields from planets. If the authors wish to discuss the magnetic fields, some mention of these previous works should be done. Significant mention about the shape of the magnetic field should also be prevalent. Furthermore, the planet is very close in to its star, and so there would likely be a complicated magnetic field structure due to the presence of the stellar magnetic field in the vicinity. This is not addressed or touched on when the authors assume the magnetic field is perpendicular to the flow of material.

If the authors want to keep a discussion of the magnetic field in the paper, this section should be significantly expanded and the caveats and assumptions more prominently listed. Otherwise, casual readers might over interpret this section to imply that a magnetic field is detected or that a magnetic field with a strength nice and similar to Jupiter's is the only possible explanation for the observable properties of the system with regards to its phase curve. It is the referee's preference however, that the magnetic field discussion is mostly scaled down or eliminated.

#

We expanded the discussion of magnetic fields according to the referee's suggestions. We think it is important to keep this section of the paper because it opens up discussion about a new way of measuring planet magnetic fields (studying their effects on the atmospheric dynamics, in contrast to previous work, which focused on star-planet interactions).  We put this discussion in a new subsection (6.1), added references to previous work, and mentioned the suggested caveats. We also clarified in the abstract that our estimate of the magnetic field is based on a back of the envelope calculation.

@@

Thank you! We are glad liked it.

****

20. Figure 16: I think the y scales on each vertical section of plots need to be adjusted to be the same. This will facilitate easier comparison than as currently shown (this is similar to my previous comments on other plots).

Our goal for this plot was to show differences in the relative flux in and out of the water feature (the amplitudes A1 and A2), rather than comparing the absolute flux. The absolute flux levels are dependent on the radius of the object -- for example, the directly imaged companions have inflated radii, so their absolute fluxes are higher.  Therefore, to make an apples-to-apples comparison between objects, we normalize the spectra by their absolute flux to calculate the indices A1 and A2.  This is why we chose not to plot all the spectra on the same absolute scale, and instead use a different y-axis for each to better illustrate the relative water feature amplitude.

@@

Our goal for this plot was to show differences in the relative flux in and out of the water feature (the amplitudes A1 and A2), rather than comparing the absolute flux. The absolute flux levels are dependent on the radius of the object -- for example, the directly imaged companions have inflated radii, so their absolute fluxes are higher.  Therefore, to make an apples-to-apples comparison between objects, we normalize the spectra by their absolute flux to calculate the indices A1 and A2.  This is why we chose not to plot all the spectra on the same absolute scale, and instead use a different y-axis for each to better illustrate the relative water feature amplitude.

****

21. I like the format of section 8 (the summary/conclusion section). The bullet points are helpful to readers that would skim through a paper and I wish more papers had done this. I would encourage the authors (if they feel like it) to bold a statement in each of the bullet points as well.

Thanks! We had trouble indentifying a single sentence in each bullet to bold, so this time we decided to leave it as is.

### 2018-04-04 ApJ_submit_v2/ms.tex
points 19

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

Here we make a simple order-of-magnitude estimate for the magnetic field required to produce a drag timescale of order $10^4$\,s. We first computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM. Using the analytic expression from \cite{perna10} (Equation 12), we estimated a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss. We assumed a temperature and pressure of 3359 K and 0.11 bar, %(FIXME use correct values for drag4) 
and that the magnetic field is perpendicular to the flow. To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required, comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.  \added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for possible complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}

>>>>

\begin{abstract}
%	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, which can be produced with a simple model of the magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

Here we make a simple order-of-magnitude estimate for the magnetic field required to produce a drag timescale of order $10^4$\,s. We first computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM. Using the analytic expression from \cite{perna10} (Equation 12), we estimated a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss. We assumed a temperature and pressure of 3359 K and 0.11 bar, %(FIXME use correct values for drag4) 
and that the magnetic field is perpendicular to the flow. To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required, comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.  \added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for the possibility of complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}
